---
title: "Waves_intact_cells"
author: "Ruben Lopez"
date: "3/26/2021"
output:
  html_document: default
  word_document: default
editor_options:
  chunk_output_type: inline
---

# Analysis of Ca^2+^ waves in intact cells



```{r, setup, echo=FALSE}
## Setting enviroment
knitr::opts_chunk$set(
  comment = '', fig.width= 6, fig.asp = 0.8, warning=FALSE, message=FALSE, results='hide', include=FALSE, echo=FALSE)
```



------------------------------------------------------------------------

```{r}

############# Importing libraries #############

pacman::p_load(AnlysisOfWaves, # custom functions for analysis and loading of additioanl libraries
               here, # folder's system navigation,
               readxl,
               purrr, dplyr, tidyr, stringr, kableExtra, # wrangling data
               broom.mixed) # tools for mixed effect model computation

options("scipen" = 999, "digits" = 4)

```



```{r}

############# Create folder and names structure #############

# name of parameters for analysis
parameters <- list("kinetics", "frequency", "occurence") %>% 
                                purrr::set_names()
parameters

# name of output directories for each parameter
output_results_dir <- map(parameters, ~(sprintf(here("results",
                               "intact_cells",
                               "wave_%s"), .x)))
   output_results_dir
# output_result


# name of output directories for figures
# output_figs_dir <- bind_cols(list(laten_and_freq = "Figures/Intact_cells/Waves_late_freq_occu" , 
#                              wave_kinet = "Figures/Intact_cells/Waves_kinetics", 
#                              combi_panel = "Figures/Intact_cells/Combined_pannel"))

   output_figs_dir <-here("figures", "Intact_cells") %>% 
     list() %>% 
     set_names(nm = "intact_cells")
    # dir.exists()
    
    
output_figs_dir$intact_cells
```


We load the excel file containing the features extracted form the linescan images. They also contain relevant additional information such as date, animal, treatments, etc.


```{r}

############# Loading the raw dataset from the excel file ############# 

df40 <-as.data.frame(read_xlsx(here("datasets", 
                                    "intact_cells",
                                    "pooled_IntactCells_WL_WS_EAP_OCC_CAFF.xlsx"),
                               sheet = 1, skip = 13))
 df40 %>% 
   head
```



```{r}

############# repare names, etc ############# 

df40 <- df40 %>% # Remove the "_mean" suffix of some variable names.
  rename_all(~str_replace(., pattern = "_mean", replacement = "")) 

df40 <- df40[-17] # remove extra column "Wave_latency"
colnames(df40) [16] <- "Wave_latency" # <- USE ONLY THIS variable for wave latency, since it's repeated
colnames(df40) [18] <-  "Wave_Freq_Hz"
colnames(df40) [24] <-  "EAP_Latency"

# transforming in s units latency and EAP
df40$Wave_latency <- df40$Wave_latency / 1000 # changing wave latency units from ms to seconds
df40$EAP_Latency <- df40$EAP_Latency / 1000 # changing EAP latency units from ms to seconds


# 5. Setting as factor several variables ----
df40$Condition[df40$Condition == "Iso_3'"] <- "ISO"
# df40$Condition <- factor(df40$Condition, levels = c("Control", "ISO"))

df40$Animal[df40$Animal == "CPVT-HET"] <- "CPVT"
df40$Animal[df40$Animal == "CPVT-WT"] <- "WT"

df40 <- df40 %>%
  # df40 %>% 
    mutate(Groups = factor(paste(Condition,
                                 Animal ,
                                 sep = "_"),
                           levels = c("Control_WT",
                                      "Control_CPVT",
                                      "ISO_WT",
                                      "ISO_CPVT"))) %>%
    mutate(across(starts_with(c("Date", "Condition", "Animal", "For")), as.factor) ) %>%
    mutate(Experiment = factor(str_sub(filename, 10, 15)),
           core_name = str_sub(filename, 1, -5),
           filename = factor(filename),
           Animal = factor(Animal, levels = c("WT", "CPVT"))) 


```


We define a time window (in seconds) threshold for later determine the occurrence of waves and frequency.

```{r}
wave_or_EAP_threshold <- 10
```

which is `r wave_or_EAP_threshold` seconds. 

### Create variables namespace

We take the columns names from the excel sheet and create the set of variables names of the various features of interest for later use.

```{r}

# this are the variables names for spontaneous waves kinetics (de-skewed)
wave_kinet_parameters <- df40 %>%
  select(starts_with("Wave_") / (contains(c("50", "late", "Freq")))) %>% 
  names() %>% 
  rev() %>% # revert order
  set_names() %>% 
  map(~.x) 


# this are the variables names for spontaneous waves occurrence and frequency
wave_lat_and_freq <- df40 %>%
  select(starts_with("Wave_") / contains("5") & ends_with(c("cy", "Hz"))) %>%
  names() %>% 
  set_names() %>% 
  map(~.x) 

# this are the variables names for spontaneous electrical-stimulated Calcium transients 
trans_kinet_parameters <- df40 %>%
  select(starts_with("Trans_") / (contains(c("50", "late", "Freq")))) %>%
  names() %>% 
  rev() %>% # revert order
  set_names() %>% 
  map(~.x) 


# log10_wave_kinet_parameters <- wave_kinet_parameters %>% 
#   names %>%
#   set_names(nm = paste0("log10_",.)) %>% 
#   map(~paste0("log10_",.x))


# this are the variables names for Caffeine-induced transients 
caff_parameters <- df40 %>%
  select(starts_with("Caff") / (contains(c("50")))) %>%
  names() %>% 
  rev() %>% # revert order
  set_names() %>% 
  map(~.x) 


```

### Keep only ok experiments

Based on the notes, We take only the subset of the dataset that were considered good for analysis, that is, successful experiments.

```{r}

#filtering: removing no responding experiments
df40$`For_Wave_Kinetics_Analysis?`[df40$core_name %in% c("20181115 L1 CS1 Cell A0002", "20190118 L2 CS4 Cell A0002", 
                                                             "20181213 L1 CS3 Cell A0001", "20181213 L1 CS3 Cell A0002")] <- "no"

# 6. Taking only the data for Occurrency analysis = yes ----

df40_o <- (subset(df40, df40$`For Occu Analysis?`== "yes"))

rm(df40)

```


And this is how it looks a subset of the the curated dataset 

```{r results='show', include=TRUE}

df40_o %>% 
  head %>% 
  kable() %>% 
  kable_styling(font_size = 7)

```


# Statistics

## Descriptive stats

We compute descriptive statistics to observe the data quality, trend, etc...

##### Wave kinetics

```{r}
# df40_o %>% 
#   filter(`For_Wave_Kinetics_Analysis?` == "yes") %>%
#   clean_and_tidy_df_func(vars_for_analysis = wave_kinet_parameters) %>% 
#   my_summ_stat_func()
```

We group and nest the data


```{r}
nested_df <- df40_o %>% 
  # mutate()
  select(!starts_with(c("Gender", "Protocol", "Chip", "notes",  "Total")) &
           !contains(c("ms", "EAP", "Age", "t50")) & 
           where(~  is.numeric(.x) || is.factor(.x))) %>% 
  # head
  # names
  # str()
  pivot_longer(cols = as.character(c(wave_kinet_parameters, wave_lat_and_freq, trans_kinet_parameters, caff_parameters)), names_to = "parameters" ) %>%
  group_by(parameters) %>% 
  nest()
  
  
nested_df%>% 
  pull(data) %>% 
  head(1)


```



YOu are here -> NOTE: to make properly the summary stats, you need first to subset the data for analysis respectively

```{r}
nested_df %>% 
  mutate(summary = map( data, ~my_summ_stat_func(.x, round_to = 2) %>% 
                          pivot_longer(where(is.double)) %>% 
                          drop_na(value) %>%
                          mutate(Parameters = str_sub(Parameters, 
                                                      start = 1, end = 5)) %>%
                          pivot_wider(values_from = value, 
                                      names_from = name))) %>% 
  pull(summary)
```
# outline 

- 1. Descriptive stats and export results 

YOu are here -> NOTE: to make properly the summary stats, you need first to subset the data for analysis respectively

- 2. Hypothesis testing (make mix model) and export results

- 3. Standard Plot and export figures

- 4. Repre traces and export results. 

- 5. render all images in this document?




