---
title: "Automatic report"
author: "Ruben Lopez"
date: "Generated on: `r format(Sys.time(), '%d.%m.%Y')`"
output:
  html_document: default
  word_document: default
editor_options:
  chunk_output_type: inline
params:
  OUTPUT: FALSE
---

# Analysis of Ca^2+^ waves in intact cells



### This document contain the following: 

- 1. [x] Descriptive statistics on wave parameters in intact cell 

- 2. [x] Hypothesis testing using linear regression with mixed effect model

- 3. [x] Superplots figures 




```{r, setup, echo=FALSE}
## Setting enviroment
knitr::opts_chunk$set(
  comment = '', fig.width= 6, fig.asp = 0.8, warning=FALSE, message=FALSE, results='hide', include=FALSE, echo=FALSE)

```

Here's my parameter: `r params$output_results`.


------------------------------------------------------------------------

```{r}

############# Importing libraries #############

# remotes::install_github("rjlopez2/AnlysisOfWaves@e3cc2a3") # custom functions for analysis and loading of additional libraries

pacman::p_load(AnlysisOfWaves, # custom functions for analysis and loading of additional libraries
               here, fs, # folder's system navigation,
               readxl,
               readr,
               cowplot,
               purrr, dplyr, tidyr, stringr, kableExtra, # wrangling data
               ggplot2, ungeviz, # piloting
               lmerTest, broom.mixed, emmeans) # tools for mixed effect model computation and multiple comparison

options("scipen" = 999, "digits" = 4)

```



```{r}
############# Create folder and names structure #############

# name of parameters for analysis
parameters <- list("kinetics", "frequency", "occurence") %>% 
                                purrr::set_names()

# name of output directories for each parameter
output_results_dir <- map(parameters[1:2], ~(sprintf(here("results",
                               "intact_cells",
                               "wave_%s"), .x)))


# name of output directories for figures

output_figs_dir <- list("kinetics", "latency_and_occu") %>% 
  purrr::set_names() %>% 
  map(~(sprintf(here("figures",
                     "intact_cells",
                     "wave_%s"), .x)))

    
# output_figs_dir$intact_cells

table_output_font_size = 10


# names for axis titles

plot_names <- list(wave_occurence = c("Cumulative occurence (%)",
                                 "Wave occurence (%)",
                                 "Wave latency (s)",
                                 "Wave frequency (Hz)"),
                   wave_kinetics = c("Amplitude (∆F/F0)",
                                     "Decay constant τ (ms)",
                                     "Velocity (µm/s)")) %>% 
  map(~set_names(.x))
```


```{r, eval=params$OUTPUT}
# Create all new directories for output results and figures

c(output_results_dir, output_figs_dir) %>% 
  map(~dir_create(path = .x))
```


We load the excel file containing the features extracted form the linescan images. They also contain relevant additional information such as date, animal, treatments, etc.


```{r}

############# Loading the raw dataset from the excel file ############# 

df40 <-as.data.frame(read_xlsx(here("datasets", 
                                    "intact_cells",
                                    "pooled_IntactCells_WL_WS_EAP_OCC_CAFF.xlsx"),
                               sheet = 1, skip = 13))
```



```{r}

############# repare names, etc ############# 

df40 <- df40 %>% # Remove the "_mean" suffix of some variable names.
  rename_all(~str_replace(., pattern = "_mean", replacement = "")) 

df40 <- df40[-17] # remove extra column "Wave_latency"
colnames(df40) [16] <- "Wave_latency" # <- USE ONLY THIS variable for wave latency, since it's repeated
colnames(df40) [18] <-  "Wave_Freq_Hz"
colnames(df40) [24] <-  "EAP_Latency"

# transforming in s units latency and EAP
df40$Wave_latency <- df40$Wave_latency / 1000 # changing wave latency units from ms to seconds
df40$EAP_Latency <- df40$EAP_Latency / 1000 # changing EAP latency units from ms to seconds


# 5. Setting as factor several variables ----
df40$Condition[df40$Condition == "Iso_3'"] <- "ISO"
# df40$Condition <- factor(df40$Condition, levels = c("Control", "ISO"))

df40$Animal[df40$Animal == "CPVT-HET"] <- "CPVT"
df40$Animal[df40$Animal == "CPVT-WT"] <- "WT"

df40 <- df40 %>%
  # df40 %>% 
    mutate(Groups = factor(paste(Condition,
                                 Animal ,
                                 sep = "_"),
                           levels = c("Control_WT",
                                      "Control_CPVT",
                                      "ISO_WT",
                                      "ISO_CPVT"))) %>%
    mutate(across(starts_with(c("Date", "Condition", "Animal", "For")), as.factor) ) %>%
    mutate(Experiment = factor(str_sub(filename, 10, 15)),
           core_name = str_sub(filename, 1, -5),
           filename = factor(filename),
           Animal = factor(Animal, levels = c("WT", "CPVT"))) 


```


We define a time window (in seconds) threshold for later determine the occurrence of waves and frequency.

```{r}
wave_or_EAP_threshold <- 10
```

which is `r wave_or_EAP_threshold` seconds. 

### Create variables namespace

We take the columns names from the excel sheet and create the set of variables names of the various features of interest for later use.

```{r}

# this are the variables names for spontaneous waves kinetics (de-skewed)
wave_kinet_parameters <- df40 %>%
  select(starts_with("Wave_") / (contains(c("50", "late", "Freq")))) %>% 
  names() %>% 
  rev() %>% # revert order
  set_names() %>% 
  map(~.x) 


# this are the variables names for spontaneous waves occurrence and frequency
wave_lat_and_freq <- df40 %>%
  select(starts_with("Wave_") / contains("5") & ends_with(c("cy", "Hz"))) %>%
  names() %>% 
  set_names() %>% 
  map(~.x) 

# this are the variables names for spontaneous electrical-stimulated Calcium transients 
trans_kinet_parameters <- df40 %>%
  select(starts_with("Trans_") / (contains(c("50", "late", "Freq")))) %>%
  names() %>% 
  rev() %>% # revert order
  set_names() %>% 
  map(~.x) 


# log10_wave_kinet_parameters <- wave_kinet_parameters %>% 
#   names %>%
#   set_names(nm = paste0("log10_",.)) %>% 
#   map(~paste0("log10_",.x))


# this are the variables names for Caffeine-induced transients 
caff_parameters <- df40 %>%
  select(starts_with("Caff") / (contains(c("50")))) %>%
  names() %>% 
  rev() %>% # revert order
  set_names() %>% 
  map(~.x) 


```

### Keep only ok experiments

Based on the notes, We take only the subset of the dataset that were considered good for analysis, that is, successful experiments.

```{r}

#filtering: removing no responding experiments
df40$`For_Wave_Kinetics_Analysis?`[df40$core_name %in% c("20181115 L1 CS1 Cell A0002", "20190118 L2 CS4 Cell A0002", 
                                                             "20181213 L1 CS3 Cell A0001", "20181213 L1 CS3 Cell A0002")] <- "no"

# 6. Taking only the data for Occurrency analysis = yes ----

df40_o <- (subset(df40, df40$`For Occu Analysis?`== "yes"))

rm(df40)

```


And this is how it looks a subset of the the full curated dataset 

```{r results='show', include=TRUE}

df40_o %>% 
  kable %>%
  kable_styling(font_size = table_output_font_size) %>% 
  scroll_box(width = "100%", height = "400px")
  # kable(format= "latex", booktabs = T) %>% 

```


### checking the files for repository ->  done 


```{r}
df40_o %>% 
  # names
  distinct(filename) %>% 
  arrange(desc(filename))
```

Finding the folder dates where the data is located and save it as an csv file.
Note: Luckily for this set of the experiment you can save the entire folder without cherry-picking specific files/subfolders. But for other datasets you may need to check.

```{r}

df40_o %>% 
  distinct(Date) %>% 
  arrange(desc(.)) %>% 
  mutate(Date = as.character(Date)) %>% 
  mutate(Date = str_sub(Date, start = -8) %>% str_replace_all(pattern = "-", "")) #%>% 
  # write_csv(file = "intact_cells_dates.csv")
```



# Statistics

## Descriptive stats

We compute descriptive statistics to observe the data quality, trend, etc...



```{r}
# df40_o %>% 
#   filter(`For_Wave_Kinetics_Analysis?` == "yes") %>%
#   clean_and_tidy_df_func(vars_for_analysis = wave_kinet_parameters) %>% 
#   my_summ_stat_func()
```

we nest the full raw dataset.


```{r}

# We group and nest the data

all_parameters = c(wave_kinet_parameters,
                   wave_lat_and_freq,
                   trans_kinet_parameters,
                   caff_parameters)


nested_df <- df40_o %>%
 select(!starts_with(c("Gender", "Protocol", "Chip", "notes",  "Total")) &
           !contains(c("ms", "EAP", "Age", "t50")) & 
           where(~  is.numeric(.x) || is.factor(.x))) %>% 
  pivot_longer(cols = as.character(all_parameters), names_to = "variables" ) %>%
  group_by(variables) %>%
  nest %>% 
    ungroup() %>%
    mutate(data = map2(data, variables, ~ mutate(.x, var_name = .y))) %>% 
  group_by(variables)
   
nested_df

```



You are here -> NOTE: to make properly the summary stats, you need first to subset the data for analysis respectively


### Wave kinetics


Compute and export summary of wave kinetics parameters

```{r}

wave_kinetics_df_nest <- nested_df %>%
  filter(variables %in% as.character(wave_kinet_parameters)) %>% #take only the datad=set for wavekinetics
  mutate(data = map(data, ~(.x %>% 
                              filter(`For_Wave_Kinetics_Analysis?` == "yes") ))) %>% 
  describe_nested_df(targed_dataset = "data")


wave_kinetics_df_nest
```

Here are the summary statistics of the wave kinetics parameters: `r as.character(wave_kinet_parameters)`

```{r results='show', include=TRUE}
wave_kinetics_df_nest %>% 
  unnest(described) %>% 
  arrange(variables, Condition) %>% 
  select(-data, -Parameters, -where(is.list)) %>% 
  # kableExtra::kable(format = "latex", booktabs = T)
  kable %>%
  kable_styling(font_size = table_output_font_size) %>% 
  collapse_rows(columns = c(1:5))
```
#### Export summry statistics results

Here we export the descriptive statistics from the wave kinetics parameters: `r as.character(wave_kinet_parameters)` and can be found in the directory: `r output_results_dir$kinetics`


```{r eval = params$OUTPUT}
wave_kinetics_df_nest %>% 
  unnest(described) %>% 
  arrange(variables, Condition) %>% 
  select(-data, -Parameters, -where(is.list)) %>% 
  write_csv(paste(output_results_dir$kinetics, 
                  paste(format(Sys.time(),
                               '%Y%m%d'),
                        "summary_stats.csv",
                        sep = "_"), sep = "/"))
```


#### QQ-plots of wave kinetics parameters


```{r, results='show', include=TRUE, collapse = TRUE, fig.width=12, fig.asp = 0.3, out.width='100%'}
wave_kinetics_df_nest %>% 
  mutate(qq_plot = map(qq_plot, ~.x +  
                         ggplot2::scale_colour_manual(values = c("#666666", 
                                                                 "#CC0000")) +
                         ggplot2::scale_fill_manual(values = c("#666666", 
                                                                 "#CC0000")) +
                         pptx_presentation_theme_func(base_size = 12))) %>% 
  pluck("qq_plot") %>% 
  plot_grid(plotlist = ., ncol = 3)
```



### Frequency and latency

```{r}
wave_freq_df_nest <- nested_df %>%
# nested_df %>%
  filter(variables %in% as.character(wave_lat_and_freq)) %>% 
  # unnest() %>%  # take only the dataet for wavekinetics
  # pivot_wider(names_from = variables, values_from = value)
  # unnest()
  # mutate(data)
  # mutate(data = map(data, ~(.x %>% 
  #                             filter(`For WL Analysis?` == "yes",
  #                                    value <= wave_or_EAP_threshold$lat_thr) ))) %>% 
  describe_nested_df(targed_dataset = "data")

wave_freq_df_nest

# nested_df$data[4][1]

```

Here are the summary statistics of the wave frequency parameters: `r as.character(wave_lat_and_freq)`

```{r results='show', include=TRUE}

wave_freq_df_nest %>% 
  unnest(described) %>% 
  arrange(variables, Condition) %>% 
  select(-data, -Parameters, -where(is.list)) %>% 
  # kableExtra::kable(format = "latex", booktabs = T)
  kable %>%
  kable_styling(font_size = table_output_font_size) %>% 
  collapse_rows(columns = c(1:5))

```

#### Export summary statistics results

Here we export the descriptive statistics from the wave Frequency parameters: `r wave_lat_and_freq` and can be found in the directory: `r output_results_dir$frequency`


```{r eval = params$OUTPUT}
wave_freq_df_nest %>% 
  unnest(described) %>% 
  arrange(variables, Condition) %>% 
  select(-data, -Parameters, -where(is.list)) %>% 
  write_csv(paste(output_results_dir$frequency, 
                  paste(format(Sys.time(),
                               '%Y%m%d'),
                        "summary_stats.csv",
                        sep = "_"), sep = "/"))
```


#### QQ-plots of wave kinetics parameters


```{r results='show', include=TRUE, collapse = TRUE, fig.width=12, fig.asp = 0.3, out.width='200%'}
wave_freq_df_nest %>% 
   mutate(qq_plot = map(qq_plot, ~.x +  
                         ggplot2::scale_colour_manual(values = c("#666666", 
                                                                 "#CC0000")) +
                         ggplot2::scale_fill_manual(values = c("#666666", 
                                                                 "#CC0000")) +
                         pptx_presentation_theme_func(base_size = 12))) %>% 
  pluck("qq_plot") %>% 
  plot_grid(plotlist = ., ncol = 3)
  # plot_grid(plotlist = ., ncol = 1)
  
  
```


## Hypothesis testing

### Testing for the wave kinetics parameters

We use mix model to describe significance in the multiples waves parameters analyzed.

Let's first define the model that describe our hypothesis which is defined by the fix effects:  Genotype (WT/CPVT) or Drug condition (Control/ISO?others..) and the random effect: Animal ID.

```{r}
nointer_mixmodel <- function(my_dataset){
  lmerTest::lmer(value ~ Animal + Condition + (1|Animal_No), 
                 data = my_dataset,
                 REML = FALSE)
}
```

We can test for a second model whit similar describers but using interaction, which in our case is the appropriate one since we expect that the genotype (WT/CPVT) is responding differently (interact) when we apply the treatment. 

```{r}
inter_mixmodel <- function(my_dataset){
  lmerTest::lmer(value ~ Animal * Condition + (1|Animal_No), 
                 data = my_dataset,
                 REML = FALSE)
}
```


```{r}
model_raw_nsdf <- wave_kinetics_df_nest %>% 
  select(data) %>% 
  apply_model_func(my_model = nointer_mixmodel) %>% 
  apply_model_func(my_model = inter_mixmodel) %>% 
  pivot_longer(cols = ends_with("model"), 
               names_to = "model_name", 
               values_to = "model")
  

# model_raw_nsdf
```

We extract information and inspect side-by-side model performance, at the left side is the model without interaction and right is the one with interaction.

```{r}
model_results_nsdf <- model_raw_nsdf %>% 
  extract_model_info_func() %>% 
  plot_residuals_func()
# model_results_nsdf

```



```{r results='show', include=TRUE, collapse = TRUE, fig.width=16, fig.asp = 0.8, out.width='200%'}
wave_kinet_parameters %>% 
  map(~(model_results_nsdf %>% 
          ungroup() %>% 
          filter(variables == .x ) %>% 
          pull(res_vs_fit_plot) %>% 
          plot_grid(plotlist = ., ncol = 2))) %>% 
  plot_grid(plotlist = ., ncol = 1)

```

The residuals looks ok, so we stick with the mix model  with interaction and start making the comparisons of the different treatments, aka we make the contrasts as describe in the following step.

### Make Contrast

#### Wave kinetics

First we design a matrix to make the desired comparisons. Here we want to compare genotypes differences among control and ISO treatment, so we design the matrix accordingly


```{r}
contrast_matrix <- list("WT_Control vs CPVT_Control" = c(1, 0, 0, 0) - c(0, 1, 0, 0),
                        "WT_ISO vs CPVT_ISO" = c(0, 0, 1, 0) - c(0, 0, 0, 1))
contrast_matrix

```


```{r}
emmens_ns_df <- model_raw_nsdf %>%
# model_raw_nsdf %>%
  # filter(str_detect(model_name, "no")) %>% 
  mutate(em_means = map2(data, model, ~ emmeans(object =  .y, 
                                                specs =  ~ Animal * Condition, 
                                                data = .x)),
         # estimates = map(em_means, ~(.x$emmeans %>%
         estimates = map(em_means, ~(.x %>%
                                       as_tibble %>%
                                       drop_na %>%
                                       mutate(across(where(is.double),
                                                     ~ round(.x, digits =2))))),
         # contrasts = map(em_means, ~(.x$contrasts %>% 
         #                               as_tibble %>% 
         #                               drop_na %>% 
         #                               mutate(across(where(is.double), 
         #                                             ~ round(.x, digits =2))))))#,
         contrast = map(em_means, ~(.x %>%
                                        contrast(method = contrast_matrix, adjust = "BH") %>%
                                       broom::tidy() %>% 
                                        mutate(across(where(is.double),
                                                      ~ round(.x, digits =2)))
                                     ))) 

```

Let's have a look at our contrast table.

```{r results='show', include=TRUE}

wave_kinetics_contras_table <- emmens_ns_df %>% 
  filter(!str_detect(model_name, "nointer")) %>% #take only the model with interaction
  select(contrast, model_name) %>% 
  unnest() %>% 
  mutate(significance = case_when(adj.p.value < 0.0001 ~ "****",
                                  adj.p.value < 0.001 ~ "***",
                                  adj.p.value < 0.01 ~ "**",
                                  adj.p.value < 0.05 ~ "*",
                                  adj.p.value > 0.05 ~ "ns",
                                  TRUE ~ as.character(adj.p.value)), .before = model_name) %>% 
  mutate(group1 = word(contrast, 1),
         group2 = word(contrast, 3)) %>% 
  pivot_longer(cols = starts_with("group"), names_to = "groups", values_to = "Condition") %>% 
  mutate(Animal = str_extract(Condition, pattern = "WT|CPVT"),
         Condition = str_extract(Condition, pattern = "Control|ISO")) %>% 
  pivot_wider(values_from = Animal, names_from = groups) %>% 
  relocate(Condition, starts_with("group"), .after = variables) %>% 
  select(-contrast) 

wave_kinetics_contras_table %>% 
  kable %>%
  kable_styling(font_size = table_output_font_size)

```
Note that this results are slightly different form those reported in the paper since there we use standard t-test to asses significance. However the conclusion is the same. Only the waves amplitude in control condition are significantly higher in the CPVT cardiomyocytes.


### Export results


Here we export the test contrast from the wave latency parameters: `r wave_kinet_parameters` and can be found in the directory: `r output_results_dir$kinetics`


```{r eval = params$OUTPUT}
wave_kinetics_contras_table %>% 
  write_csv(paste(output_results_dir$kinetics, 
                  paste(format(Sys.time(),
                               '%Y%m%d'),
                        "test_stats.csv",
                        sep = "_"), sep = "/"))
```




# Ploting 

## Superplots

Superplots are plots that try to represent the real distribution and sampling of a given dataset or experimental conditions. In our case we plot number of cells and number of animals. Additionally we draw theoretical distribution of our dataset. For more information please read the reference number [24] from the paper or this [link](https://doi.org/10.1083/jcb.202001064). 

### Kinetics parameters

Here we plot the wave kinetics parameters namely: `r plot_names$wave_kinetics[1:2]` and `r plot_names$wave_kinetics[3]`. Big circles are animal numbers that presented waves. Small circles are cells. The violin plot are estimated values from a gaussian distribution resampling. The horizontal bar on top of each plots are mean values respectively.

```{r}
wave_kinetics_df_nest
```

```{r, results='show', include=TRUE, collapse = TRUE, fig.width=12, fig.asp = 0.3, out.width='200%'}

wave_kinetics_df_nest <- wave_kinetics_df_nest %>%
# wave_kinetics_df_nest %>%
  ungroup() %>% 
  mutate(superplots = map2(data, plot_names$wave_kinetics, ~ {.x %>% superplot_func(yaxe = "value", 
                                                                     base_violin = "cells",
                                                                     dot_layer = "cells",
                                                                     animal_layer = T,
                                                                     wave_alpha = 0.1,
                                                                     wave_size = 1,
                                                                     cell_size = 2,
                                                                     cell_alpha = 0.2,
                                                                     jitter_width_cell = 4,
                                                                     animal_size = 5,
                                                                     animal_alpha = 0.6,
                                                                     line_size = 1,
                                                                     # base_font_size = 20, #this is the original valu
                                                                     base_font_size = 12,
                                                                     trim = FALSE,
                                                                     scaled_to = "width",
                                                                     adjusted = 1.5) + 
      ggplot2::ylab(label = .y) + 
    geom_hpline(stat = "summary", aes(color = Animal)) # add this line if you want to add average vertical line
    })) 



wave_kinetics_df_nest$superplots %>% 
  plot_grid(plotlist = .,
            ncol = 3, labels = "AUTO")

```

```{r eval = params$OUTPUT}
######### Save your plot ##########
walk2(wave_kinet_parameters,
      wave_kinetics_df_nest$superplots,
      ~ ggsave(plot = .y, filename = paste(output_figs_dir$kinetics,
                                           paste(format(Sys.Date(),
                                                        "%y%m%d"),
                                                 paste0(.x,".pdf"),
                                                 sep = "_"),
                                           sep = "/"),
               device = "pdf",
               units = "cm",
               width = 12,
               height = 11))

```



### Latency/Frequency parameters

Here we plot the wave frequency and occurrence parameters namely: `r plot_names$wave_occurence[1:3]` and `r plot_names$wave_occurence[4]`. Panel **A** is the cumulative occurrence of the full recording (40 s) indicating the time window chosen for the next plots. Cutoff is at 10 s. Panel **B** is the occurrence of waves at 10 s. Pannel **C** and **D** are wave latency and frequency respectively at such time point.

```{r, results='show', include=TRUE, collapse = TRUE, fig.width=12, fig.asp = 0.6, out.width='200%'}

wave_or_EAP_threshold = list(lat_thr = 10,
                             freq_thr = NULL)

wave_freq_df_nest <- wave_freq_df_nest%>% 
  # create superplots
  ungroup %>%
  mutate(superplots = map2(data, variables, ~ {.x %>% 
      filter(`For WL Analysis?` == "yes", # important! filter this value so you get the correct thresholded plot 
             value <= 10) %>% 
      superplot_func(yaxe = "value", 
                     base_violin = "cells",
                     dot_layer = "cells",
                     animal_layer = T,
                     wave_alpha = 0.1,
                     wave_size = 1,
                     cell_size = 2,
                     cell_alpha = 0.2,
                     jitter_width_cell = 4,
                     animal_size = 5,
                     animal_alpha = 0.6,
                     line_size = 1,
                     # base_font_size = 20, #this is the original value
                     base_font_size = 12,
                     trim = FALSE,
                     scaled_to = "width",
                     adjusted = 1.5) + 
      ggplot2::ylab(.y) + 
      geom_hpline(stat = "summary", aes(color = Animal))}),
      # create cumulative occurrence 
      cum_occu_plot = pmap(list(data, wave_or_EAP_threshold, variables), 
                           function(.x, .y, .z){.x %>% 
                               my_cum_occu_wave_plot_func( 
                                 reffer_wave_thres = .y,
                                 my_var = "value", 
                                 # base_size = 20, #this is the original value
                                 base_size = 12, 
                                 line_size = 2) + ggplot2::ylab(.z)}),
      # create barplot with wave occurence
      occu_bar_plot = map(data, ~ my_occu_bar_plot_func(.x,  my_var = "value", 
                                                        reffer_wave_thres = wave_or_EAP_threshold$lat_thr, 
                                                        line_size = 1, 
                                                        # base_size = 20))
                                                        base_size = 12))
  )  



wave_freq_df_nest %>% 
  pivot_longer(cols = contains("plot"), names_to = "plot_type", values_to = "plot_object") %>% 
  filter(!str_detect(plot_type, "qq")) %>% 
  arrange(plot_type) %>% 
  slice(1, 3, 5:6) %>%
  pull(plot_object) %>% 
  map2(plot_names$wave_occurence, ~ .x + ggplot2::ylab(label = .y)) %>% 
  plot_grid(plotlist = .,
            ncol = 3, 
            labels = "AUTO")
```

```{r eval = params$OUTPUT}
######### Save your plot ##########

wave_freq_df_nest %>% 
  pivot_longer(cols = contains("plot"), names_to = "plot_type", values_to = "plot_object") %>% 
  filter(!str_detect(plot_type, "qq")) %>% 
  arrange(plot_type) %>% 
  slice(1, 3, 5:6) %>%
  pull(plot_object) %>% 
  map2(plot_names$wave_occurence, ~ .x + ggplot2::ylab(label = .y)) %>% 
  # plot_grid(plotlist = .,
  #           ncol = 3, 
  #           labels = "AUTO") #%>% 
  walk2(.x = ., .y =str_replace(str_trim(str_replace(plot_names$wave_occurence, # remove special characters for creating valid dir names
                                                     pattern = "\\(.*?\\)", 
                                                     replacement = ""), 
                                         side = "right"),
                                " ", "_") , 
        ~ ggsave(plot = .x, filename = paste(output_figs_dir$latency_and_occu,
                                             paste(format(Sys.Date(),
                                                          "%y%m%d"),
                                                   paste0(.y,".pdf"),
                                                   sep = "_"),
                                             sep = "/"),
                 device = "pdf",
                 units = "cm",
                 width = 12,
                 height = 11))





  # str_trim(side = "right") %>% 

```

\

<center>FIN</center>

\
\
\


