---
title: "Waves_intact_cells"
author: "Ruben Lopez"
date: "3/26/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

# Analysis of Ca^2+^ waves in intact cells

## Importing libraries

We import the custom made package containing the functions and methods for the analysis of calcium waves.

The package `{AnlysisOfWaves}` can be download like by un-comment the following chunk code:

``` {.r}
# install.packages("devtools")
# devtools::install_github("rjlopez2/AnlysisOfWaves")
```

------------------------------------------------------------------------

```{r, global-options, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(fig.width= 12, fig.asp = 0.5,
                      echo=FALSE, warning=FALSE, message=FALSE)
if (!require("pacman")) 
  install.packages("pacman")

pacman::p_load(AnlysisOfWaves, # custom functions for analysis
               readxl, # read excel files
               tidyverse, # data wrangling
               ggpubr, ggbeeswarm, ggnewscale, colorspace, cowplot,# for data visualization
               here, # folder's system navigation,
               # lme4, 
               broom.mixed) # tools for mixed effect model computation

options("scipen" = 999, "digits" = 4)

```

## Create folder names to save results and plots

```{r}
# wave kinetics results folder
output_results_wave_kinetics <- here("output_results",
                                     "intact_cells",
                                     "wave_kinetics")

# wave frequency results folder
output_results_wave_frequency <- here("output_results",
                                     "intact_cells",
                                     "wave_frequency")

# wave frequency results folder
output_results_wave_occurence <- here("output_results",
                                     "intact_cells",
                                     "wave_occurence")

```

## Loading the raw dataset from the excel file.

This excel file contain the features extracted form the linescan images. They also contain relevant information such date, animal, treatments, etc.

Features from the wave kinetics analysis were aggregated as average in this dataset. Later on we will load the raw individual values for the kinetics.

```{r}

df40 <-as.data.frame(read_xlsx(here("raw_data", 
                                    "Cyto_waves",
                                    "pooled_IntactCells_WL_WS_EAP_OCC_CAFF.xlsx"),
                               sheet = 1, skip = 13))
 df40
```

### Reformatting the dataset, repairing names, etc...

```{r}

df40 <- df40 %>% # Remove the "_mean" suffix of some variable names.
  rename_all(~str_replace(., pattern = "_mean", replacement = ""))

df40 <- df40[-17] # remove extra column "Wave_latency"
colnames(df40) [16] <- "Wave_latency" # <- USE ONLY THIS variable for wave latency, since it's repeated
colnames(df40) [18] <-  "Wave_Freq_Hz"
colnames(df40) [24] <-  "EAP_Latency"

# transforming in s units latency and EAP
df40$Wave_latency <- df40$Wave_latency / 1000 # changing wave latency units from ms to seconds
df40$EAP_Latency <- df40$EAP_Latency / 1000 # changing EAP latency units from ms to seconds


# 5. Setting as factor several variables ----
df40$Condition[df40$Condition == "Iso_3'"] <- "ISO"
df40$Condition <- factor(df40$Condition, levels = c("Control", "ISO"))

df40$Animal[df40$Animal == "CPVT-HET"] <- "CPVT"
df40$Animal[df40$Animal == "CPVT-WT"] <- "WT"

df40$Animal <- factor(df40$Animal, levels = c("WT", "CPVT"))
df40$Animal_No <- factor(df40$Animal_No)

df40$Date <- as.factor(df40$Date)


# 6. making  new vector in my dataframe with the 4 experimental different groups 

df40$Groups <- paste(df40$Condition, df40$Animal, sep = "_")
df40$Groups <- factor(df40$Groups, levels = c("Control_WT", 
                                                "Control_CPVT",
                                                "ISO_WT",
                                                "ISO_CPVT"))

df40 <- df40 %>% 
     mutate(Experiment = factor(str_sub(filename, 10, 15)),
            core_name = str_sub(filename, 1, -5))
```
