---
title: "Automatic report"
author: "Ruben Lopez"
date: "Generated on: `r format(Sys.time(), '%d.%m.%Y')`"
output:
  html_document: default
  word_document: default
editor_options:
  chunk_output_type: inline
params:
  OUTPUT: FALSE
---

# Analysis of Ca^2+^ waves in permeabilized cells

### This document contain the following: 

- 1. [x] Descriptive statistics on wave parameters in intact cell 

- 2. [x] Hypothesis testing using linear regression with mixed effect model

- 3. [x] Superplots figures 


```{r, setup, echo=FALSE}
## Setting enviroment
knitr::opts_chunk$set(
  comment = '', fig.width= 6, fig.asp = 0.8, warning=FALSE, message=FALSE, results='hide', include=FALSE, echo=FALSE)
```



------------------------------------------------------------------------

```{r}

############# Importing libraries #############

pacman::p_load(AnlysisOfWaves, # custom functions for analysis and loading of additional libraries
               here, fs, # folder's system navigation,
               readxl,
               readr,
               cowplot,
               purrr, dplyr, tidyr, stringr, kableExtra, # wrangling data
               ggplot2, ungeviz, # piloting
               lmerTest, broom.mixed, emmeans) # tools for mixed effect model computation and multiple comparison

options("scipen" = 999, "digits" = 4)

# change this variable to FALSE if no output results desired

params$OUTPUT
```


```{r}
############# Create folder and names structure #############

# name of parameters for analysis
parameters <- list("kinetics", "frequency") %>% 
                                purrr::set_names()


# name of output directories for each parameter
output_results_dir <- map(parameters, ~(sprintf(here("results",
                               "perme_cells",
                               "wave_%s"), .x)))

# name of figure directories for each parameter
output_figs_dir <- map(parameters, ~(sprintf(here("figures",
                                                  "perme_cells",
                                                  "wave_%s"), .x)))
```


```{r, eval=params$OUTPUT}

# Create all new directories for output results and figures
c(output_results_dir, output_figs_dir) %>% 
  map(~dir_create(path = .x))

```


```{r}

# determine standard font size
table_output_font_size = 10

```





# Read and format the dataset on Ca^2+^ waves from permeabilized cells

```{r}

raw_data_df <- read_csv(here("datasets",
                             "perme_cells",
                             "cyto_signal_only",
                             "raw_data_perme_cells.csv"), col_types = cols(Date = col_character())) %>% 
  select(Date, Animal_No, Animal, Experiment, Linescan, Wave_No,
         Treatment, Condition, Inc_time_min,  # select only relevant variables for analysis
         starts_with("Cyto"), Freq_waves_Hz, -Cyto_Notes, -Cyto_T50, For_Analysis) %>% 
  mutate(Inc_time_min = as.integer(Inc_time_min),
         Animal_No = as.factor(Animal_No))  %>% # Set to no-double this column to avoid  problems later with computation on it.
  filter(!Inc_time_min %in% c(3)) # exclude data of 3' drug incubation time.

raw_data_df$Animal[raw_data_df$Animal == "CPVT-WT"] <- "WT"
raw_data_df$Animal[raw_data_df$Animal == "CPVT-HET"] <- "CPVT"

raw_data_df$Animal <- factor(raw_data_df$Animal, levels = c("WT", "CPVT"))
raw_data_df$Condition <- factor(raw_data_df$Condition, levels = c("Control", "cAMP", "Fab", "Vehicle"))
raw_data_df$Treatment <- factor(raw_data_df$Treatment, levels = c("Fab", "cAMP", "Vehicle"))

raw_data_df <-  raw_data_df %>% rename(Cyto_WaveSpeed = Cyto_Wave_Speed)



# setting the variable names for later use on analysis

wave_parameters <- raw_data_df %>% 
  names %>% 
  str_subset("Cyto|Freq") %>% 
  set_names() %>% 
  sort() %>% 
  map(~.x)
  
```


# Filter experiments out that didn't go well.


```{r}
cleaned_df <- raw_data_df %>%
  filter_SR_experiment_func(my_date = "2020-01-29", # outlier= DFF0 & Tau too large
                        my_Experiment = "P2 CS2",
                        set_True = F) %>%

  filter_SR_experiment_func(my_date = "2020-01-30",  # outlier -> tau too large in control (last exp of day)
                        my_Experiment = "P4 CS4",
                        set_True = F) %>%

  filter_SR_experiment_func(my_date = "2020-03-03",  # tau no changed on fab treatment
                        my_Experiment = c("P2 CS3"),
                        set_True = F) %>%

  filter_SR_experiment_func(my_date = "2020-03-03", # outlier -> tau too large in control
                        my_Experiment = c("P1 CS2"),
                        set_True = F) %>%

  filter_SR_experiment_func(my_date = "2020-01-30", # outlier -> tau too large in control
                        my_Experiment = c("P3 CS2"),
                        set_True = F) %>%

  filter_SR_experiment_func(my_date = "2020-01-28",  # outlier -> tau too large in control
                        my_Experiment = "P4 CS3",
                        set_True = F) %>%

  filter_SR_experiment_func(my_date = "2020-01-24",  # outlier -> ∆FF0 too low in control
                        my_Experiment = "P6 CS4",
                        set_True = F) %>%
  filter_SR_experiment_func(my_date = "2020-01-29",  # outlier -> Fab to strong or something wrong with this prep
                        my_Experiment = "P3 CS2",
                        set_True = F) %>%
  filter_SR_experiment_func(my_date = "2020-01-29",  # outlier -> Fab to strong or something wrong with this prep
                        my_Experiment = "P4 CS3",
                        set_True = F) %>%
  filter_SR_experiment_func(my_date = "2020-01-29",  # outlier -> Fab to strong or something wrong with this prep
                        my_Experiment = "P5 CS1",
                        set_True = F) %>%
  filter_SR_experiment_func(my_date = "2020-01-30",  # outlier -> Fab to strong or something wrong with this prep
                        my_Experiment = "P2 CS1",
                        set_True = F) %>%
  filter_SR_experiment_func(my_date = "2020-01-30",  # outlier -> Fab to strong or something wrong with this prep
                        my_Experiment = "P1 CS2",
                        set_True = F) %>%
  filter_SR_experiment_func(my_date = "2020-01-30",  # outlier -> Fab to strong or something wrong with this prep
                        my_Experiment = "P2 CS3",
                        set_True = F) %>%
  filter_SR_experiment_func(my_date = "2020-03-06",  # outlier -> Fab to strong or something wrong with this prep
                            my_Experiment = "P3 CS3",
                            set_True = F) %>%
  filter_SR_experiment_func(my_date = "2020-01-29",  # outlier -> Amplitude of Control too high or something wrong with this prep
                            my_Experiment = "P4 CS1",
                            set_True = F) %>%
  filter(For_Analysis == TRUE)  # take only valid experiments
  
  
cleaned_df
```


### checking the files for repository ->  to be done

# Statistics

## Descriptive stats


We compute descriptive statistics to observe the data quality, trend, etc...


```{r}

nested_df <- cleaned_df %>%
  filter(Treatment != "Vehicle") %>% 
  # cleaned_df %>%
  pivot_longer(cols = matches("Cyto|Freq"), names_to = "variables", values_to = "value") %>% 
  group_by(variables) %>% 
  arrange(variables) %>% 
  nest() %>% 
  ungroup() %>%
  mutate(data = map2(data, variables, ~ mutate(.x, var_name = .y))) %>% 
  rename(raw_data = data) %>% 
  # pluck("raw_data", 3)
  group_by(variables) %>%
  mutate(by_cell_data = map2(raw_data, variables, ~ .x %>% 
                               summarize_sr_by_cell_func() %>%  #)) %>%
                               # pluck("summ_by_cell")
                               clean_and_tidy_df_func(vars_for_analysis = "value") %>% 
                               mutate(var_name = .y))) %>% 
  describe_nested_df(targed_dataset = "by_cell_data", faceted_by_1 = "Treatment + Condition")
  


nested_df
```


### Wave kinetics


Here are the summary statistics of the wave kinetics parameters: `r as.character(wave_parameters)[1:3]`

```{r results='show', include=TRUE}
nested_df %>% 
  group_by(described, .add = T) %>% 
  select(-where(is.list)) %>% 
  unnest(described) %>%
  select(-Parameters) %>% 
  # pull(described) %>% 
  relocate(variables, .before = Animal) %>%
  filter(!str_detect(variables, "Freq")) %>% 
  ungroup() %>% 
  kable(format = "html") %>%
  kable_styling(font_size = table_output_font_size) %>% 
  collapse_rows(columns = c(1:3, 5:6))
```

### Wave Frequency


Here are the summary statistics of the wave frequency paramter: `r as.character(wave_parameters)[4]`

```{r results='show', include=TRUE}
nested_df %>% 
  group_by(described, .add = T) %>% 
  select(-where(is.list)) %>% 
  unnest(described) %>%
  select(-Parameters) %>% 
  # pull(described) %>% 
  relocate(variables, .before = Animal) %>% 
  filter(str_detect(variables, "Freq")) %>% 
  ungroup() %>% 
  arrange(variables, Treatment) %>% 
  kable %>%
  kable_styling(font_size = table_output_font_size) %>% 
  collapse_rows(columns = c(1:6))
```




#### Export all summary statistics results

Here we export the descriptive statistics from the wave kinetics parameters: `r as.character(wave_parameters)` and can be found in the following directories `r as.character(output_results_dir)` 

```{r, eval=params$OUTPUT}

pwalk(list(data = nested_df$described,
           names = nested_df$variables,
           dirs = c(rep(output_results_dir[1], 3),
                    output_results_dir[2])), 
      function(data, names, dirs) {
        data %>% 
          mutate(Parameters = names) %>%
          write_csv(paste(dirs, 
                          paste(format(Sys.time(),
                                       '%Y%m%d'),
                                names,
                                "summary_stats.csv",
                                sep = "_"), sep = "/"))})

```



```{r}
nested_df$outliers
```

#### QQ-plots of wave kinetics parameters


```{r, results='show', include=TRUE, collapse = TRUE, fig.width=12, fig.asp = 1, out.width='100%'}
nested_df %>% 
  mutate(qq_plot = map(qq_plot, ~.x +  
                         ggplot2::scale_colour_manual(values = c("#666666", 
                                                                 "#CC0000")) +
                         ggplot2::scale_fill_manual(values = c("#666666", 
                                                                 "#CC0000")) +
                         pptx_presentation_theme_func(base_size = 12))) %>% 
  pluck("qq_plot") %>% 
  plot_grid(plotlist = ., ncol = 1)
```


## Hypotesis testing

We use mix model to describe significance in the multiples waves parameters analyzed.

Let's first define the model that describe our hypothesis which is defined by the fix effects:  Genotype (WT/CPVT) or Drug condition (Control/Fab/cAMP) and the random effect: Animal ID.


```{r}
# Model 1. mixed linear model with only Animal level (no interaction)

nointer_mixmodel <- function(my_dataset){
  lmerTest::lmer(value ~  Animal + (Treatment / Condition) + (1|Animal_No), 
                 data = my_dataset,
                 REML = FALSE)
}

# Model 5. mixed linear model with Animal level * with interaction

inter_mixmodel <- function(my_dataset){
  lmerTest::lmer(value ~ Animal * Treatment * Condition + (1|Animal_No), 
                 data = my_dataset,
                 REML = FALSE)
}
```


We apply the model and check the output

```{r}
nested_df$by_cell_data
```


```{r}
model_raw_nsdf <- nested_df %>% 
# nested_df %>%
  select(by_cell_data) %>%
  apply_model_func(targed_dataset = "by_cell_data", my_model = nointer_mixmodel) %>%
  apply_model_func(targed_dataset = "by_cell_data", my_model = inter_mixmodel) %>% 
  pivot_longer(cols = ends_with("model"), 
               names_to = "model_name", 
               values_to = "model")

```



We extract information and inspect side-by-side model performance, at the left side is the model without interaction and right is the one with interaction.

```{r}
model_results_nsdf <- model_raw_nsdf %>% 
  extract_model_info_func() %>% 
  plot_residuals_func()
```

```{r results='show', include=TRUE, collapse = TRUE, fig.width=16, fig.asp = 0.8, out.width='200%'}
wave_parameters %>% 
  map(~(model_results_nsdf %>% 
          ungroup() %>% 
          filter(variables == .x ) %>% 
          pull(res_vs_fit_plot) %>% 
          plot_grid(plotlist = ., ncol = 2))) %>% 
  plot_grid(plotlist = ., ncol = 1)

```



# Ploting 

## Superplots

### Kinetics parameters

```{r}
# nested_df %>% 
#   pluck("by_cell_data", 1) 
```


```{r, results='show', include=TRUE, collapse = TRUE, fig.width=12, fig.asp = 0.3, out.width='200%'}

nested_df %>% 
  filter(!str_detect(variables, "log|Freq")) %>% # fix var set names to avoid doing this every time
  mutate(superplots = map2(by_cell_data,  variables, ~ {.x %>% 
      filter(Condition != "Control") %>%
      
      # plot_arrange_by_condition_func(var ="value",
      #                            my_conditions = c("Fab", "cAMP"),
      #                            # my_conditions = c("Fab","cAMP"),
      #                            type_of_plot = "superplot",
      #                            faceted_by_1 = "Treatment + Condition",
      #                            base_violin = "cells",
      #                            dot_layer = "none",
      #                            animal_layer = T,
      #                            line_size = 1.5,
      #                            # wave_alpha = 0.4,
      #                            # wave_size = 2.5,
      #                            cell_size = 2.5,
      #                            cell_alpha = 0.4,
      #                            animal_size = 7,
      #                            animal_alpha = 0.7,
      #                            y_limits = 13,
      #                            base_font_size = 36) +
      
      superplot_func(yaxe = "value",
                     faceted_by_1 = "Treatment",
                     base_violin = "cells",
                     dot_layer = "cells",
                     animal_layer = T,
                     wave_alpha = 0.1,
                     wave_size = 1,
                     cell_size = 2,
                     cell_alpha = 0.2,
                     jitter_width_cell = 4,
                     animal_size = 5,
                     animal_alpha = 0.6,
                     line_size = 1,
                     base_font_size = 20, #this is the original valu
                     # base_font_size = 12,
                     trim = FALSE,
                     scaled_to = "width",
                     adjusted = 1.5) +
      ggplot2::ylab(.y) +
      geom_hpline(stat = "summary", aes(color = Animal)) # add this line if you want to add average vertical line
  })) %>% 
  pluck("superplots") %>% 
  plot_grid(plotlist = .,
            ncol = 3)

```

### Frequency parameters

```{r, eval=params$OUTPUT, results='show', include=TRUE, collapse = TRUE, fig.width=12, fig.asp = 0.3, out.width='200%'}

nested_df %>% 
  filter(!str_detect(variables, "log|Freq")) %>% # fix var set names to avoid doing this every time
  mutate(superplots = map2(by_cell_data,  variables, ~ {.x %>% 
      filter(Condition != "Control") %>%
      
      # plot_arrange_by_condition_func(var ="value",
      #                            my_conditions = c("Fab", "cAMP"),
      #                            # my_conditions = c("Fab","cAMP"),
      #                            type_of_plot = "superplot",
      #                            faceted_by_1 = "Treatment + Condition",
      #                            base_violin = "cells",
      #                            dot_layer = "none",
      #                            animal_layer = T,
      #                            line_size = 1.5,
      #                            # wave_alpha = 0.4,
      #                            # wave_size = 2.5,
      #                            cell_size = 2.5,
      #                            cell_alpha = 0.4,
      #                            animal_size = 7,
      #                            animal_alpha = 0.7,
      #                            y_limits = 13,
      #                            base_font_size = 36) +
      
      superplot_func(yaxe = "value",
                     faceted_by_1 = "Treatment",
                     base_violin = "cells",
                     dot_layer = "cells",
                     animal_layer = T,
                     wave_alpha = 0.1,
                     wave_size = 1,
                     cell_size = 2,
                     cell_alpha = 0.2,
                     jitter_width_cell = 4,
                     animal_size = 5,
                     animal_alpha = 0.6,
                     line_size = 1,
                     base_font_size = 20, #this is the original valu
                     # base_font_size = 12,
                     trim = FALSE,
                     scaled_to = "width",
                     adjusted = 1.5) +
      ggplot2::ylab(.y) +
      geom_hpline(stat = "summary", aes(color = Animal)) # add this line if you want to add average vertical line
  })) %>% 
  pluck("superplots") %>% 
  # plot_grid(plotlist = .,
  #           ncol = 2) %>% 
    ########## Save your plot ########## 
walk2(c("normalized_wave_freq_all"),
      ~ ggsave(plot = .x, filename = paste(output_figs_dir$frequency,
                                           paste(format(Sys.Date(),
                                                        "%y%m%d"),
                                                 paste0(.y,
                                                        ".pdf"),
                                                 sep = "_"),
                                           sep = "/"),
               device = "pdf",
               units = "cm",
               width = 24,
               height = 14))





```



