---
title: "Automatic report"
author: "Ruben Lopez"
date: "Generated on: `r format(Sys.time(), '%d.%m.%Y')`"
output:
  html_document: default
editor_options:
  chunk_output_type: inline
params:
  output_results: FALSE
---

# Analysis of luminal SR Ca^2+^ in permeabilized cells

### This document contain the following: 

- 1. [x] Descriptive statistics on wave parameters in intact cell 

- 2. [x] Hypothesis testing using linear regression with mixed effect model

- 3. [x] Superplots figures 


```{r, setup, echo=FALSE}
## Setting enviroment
knitr::opts_chunk$set(
  comment = '', fig.width= 6, fig.asp = 0.8, warning=FALSE, message=FALSE, results='hide', include=FALSE, echo=FALSE)
```

your parameter `r params$output_results`

------------------------------------------------------------------------

```{r}

############# Importing libraries #############

pacman::p_load(AnlysisOfWaves, # custom functions for analysis and loading of additional libraries
               here, fs, # folder's system navigation,
               readxl,readr,
               cowplot,
               dplyr, tidyr, purrr, stringr, forcats, # io of tabular files,
               # cowplot,
               # purrr, dplyr, tidyr, stringr, kableExtra, # wrangling data
               # ggplot2, ungeviz, # piloting
               lmerTest, broom.mixed, emmeans) # tools for mixed effect model computation and multiple comparison

options("scipen" = 999, "digits" = 4)


```


# define variable namespace for ploting and directories

```{r}

SR_parameters <- c("SR_tau", "SR_DFF0", "SR_Baseline") %>% 
  rlang::set_names()

# experiment_dir <- "/Volumes/RUBEN FILES/Ruben/Work/GroupNiggli/Confocal/%s/SR_experiments"
# years <- c(2019, 2021, 2022)
# expe_dir_list <- map_chr(years, ~ sprintf(experiment_dir, .x))

```


## Load the Newest* local SR raw data from the csv file. 

NOTE: Check always the last date!!!


```{r}
raw_sr_data <- read_csv(file = paste(here("datasets",
                                          "perme_cells",
                                          "SR_calcium",
                                          paste("2022-03-17",
                                                "SR_raw_data.csv", sep = "_"))), # Check always the last date!!!
                        col_types = str_c(c(rep("f", 11), # convert to factors collumns 1 to 11
                                            "_", # skip column "Blank_SR_col"
                                            rep("d", 4)), # coerce to double the numeric variables
                                          collapse = "")) %>% 
  mutate(Animal = fct_relevel(Animal, "CPVT-HET", after = 1))

raw_sr_data %>% 
  glimpse()

# levels(raw_sr_data$Animal)
```

# cleaning raw dataset

```{r}
raw_sr_data <- raw_sr_data %>% 
  filter(Condition != "Control") %>% # remove control and old experiments with 3 min incubation
  filter(!Inc_time_min %in% c(3)) %>% # remove control and old experiments with 3 min incubation
  select(-Treatment) %>% # remove repeated column
  filter(!(Date == "2019-10-25" & Experiment == "P2 CS3")) %>% # in this experiment cells did not react to drug (Fab)
  filter(!(Date == "2019-10-22" & Experiment == "P4 CS2")) %>% # this is a very obvious outlier in the dataset.
  filter(!(Date == "2019-10-31" & Experiment == "P3 CS3"))  %>% # Movement at caffeine application. Removed from dataset (vehicle).
  filter(!(Date == "2022-02-02" & Experiment == "P4 CS4"))  # this is an outlier in the dataset (vehicle)

```


# aggregate by cell



```{r}

by_cell_df <- raw_sr_data %>% 
  summarize_sr_by_cell_func()

by_cell_df %>% 
  glimpse()
```

# 4. Load Miguel data alone and join with your aggregated-by-cell dataset

## load Miguel's data

```{r}
Migule_SR_df <- read_csv(here("datasets",
                              "perme_cells",
                              "SR_calcium",
                              "2022-01-07_Miguel_SR_measurements.csv"),
                         col_types = str_c(c(rep("f", 6), 
                                             rep("d", 3)), 
                                           collapse = ""),
                         show_col_types = FALSE) %>% 
  add_Treatment_factor_func() %>% 
  mutate(Treatment = factor(Treatment)) %>% # set to factor treatment
  rename_with(~ str_sub(.x, end = -6), .cols = ends_with("mean")) # remove sufix of colnames


## join Miguel and your aggregated dataset


pooled_sr_df <- by_cell_df %>% 
  left_join(select(Migule_SR_df, -Treatment))

pooled_sr_df %>%
  glimpse()

```

# Create the permeabilization variable again for later be introduced in the mix model

```{r}

pooled_sr_df <- pooled_sr_df %>% 
  # mutate(Permeabilization = str_sub(Experiment, start = 1, end = 2))
  mutate(permeabilization = factor(paste(Animal_No, str_sub(Experiment, start = 1, end = 2), sep = "_"))) 

```


### checking the files for repository (take only your dataset) ->  done 

```{r}
by_cell_df %>% 
  names
```


```{r}
by_cell_df %>% 
  # names
  # distinct(filename) %>% 
  distinct(Date) %>%
  arrange(desc(.))
```

```{r, eval=FALSE}
by_cell_df %>%
  distinct(Date) %>%
  arrange(desc(.)) %>%
  mutate(Date = as.character(Date)) %>%
  mutate(Date = str_sub(Date, start = -8) %>% str_replace_all(pattern = "-", "")) %>%
  write_csv(file = "SR_calcium_dates.csv")
```

# Create the permeabilization variable again for later be introduced in the mix model

```{r}

pooled_sr_df <- pooled_sr_df %>% 
  # mutate(Permeabilization = str_sub(Experiment, start = 1, end = 2))
  mutate(permeabilization = factor(paste(Animal_No, str_sub(Experiment, start = 1, end = 2), sep = "_"))) 

```


# 6.1 Hirarchical test

## Nest the df to asses asumption:

- Independedncy (done)
- No outliers 
- Normality -> ok
- qq plot (only visual)
- Homogeneity of variance: this is not assumed, so we apply simple transformation to the mean and center the dat to check if impreve model performance.


 
 
```{r}
nested_df <- pooled_sr_df %>%
# pooled_sr_df %>%
  
  # names
  pivot_longer(cols = where(is.double), names_to = "Parameters", ) %>% 
  group_by(Parameters) %>% 
  nest() %>% 
  rename(raw_data = data) %>% 
   # apply a transformation of the data = centering the dataset around the mean
  mutate(centered_data = map(raw_data, ~ .x %>%
                               group_by(Animal, Condition) %>%
                               mutate(value = value - mean(value)) %>% 
                               ungroup)) %>% 
  mutate(log10_data = map(raw_data, ~ .x %>%
                               group_by(Animal, Condition) %>%
                               mutate(value = log10(value)) %>% 
                               ungroup)) %>% 
  filter(Parameters == "SR_Baseline") %>% 
  pivot_longer(cols = ends_with("data"), names_to = "dataset_type", values_to = "data")

# nested_df %>%
#   # pull(log10_data)
#   pull(data)
  # pull(centered_data)
```


## Create helper function to apply models
 
```{r}

apply_model_func <- function(dataset,
                             my_var = "data",
                             my_model){
  my_var <- sym(my_var)

  dataset %>%
    mutate("{{my_model}}" := purrr::map(!!my_var, my_model))# %>%

}


```
 
```{r}

levn_test <- function(my_dataset){
  car::leveneTest(value ~ Animal * Condition, data = my_dataset) # *** NOTE: from the description: If y is a linear-model object or a formula, the variables on the right-hand-side of the model must all be factors and must be completely crossed
  # bartlett.test(value ~ interaction(Animal , Condition), data = my_dataset)
}

```
 

# 6.2 Describe and transform nested data: exploratory analysis
 
```{r}

nested_processed <- nested_df %>% 
  describe_nested_df("data") #%>% 
  
nested_processed

```

Q-Q plots


```{r, results='show', include=TRUE, collapse = TRUE, fig.width=12, fig.asp = 1, out.width='100%'}
nested_processed %>% 
  ungroup() %>% 
  filter(dataset_type == "raw_data") %>% 
  pull(qq_plot) %>% 
  plot_grid(plotlist = ., ncol = 1)
```

Outliers

```{r}
 nested_processed %>% 
  filter(Parameters == "SR_Baseline") %>%
  
    pluck("outliers")
    # pluck("described")
    # pluck("qq_plot")
```


Homogeneity of Variance 

NOTE: for get about for the moment.

```{r}
 nested_processed %>% 
  filter(Parameters == "SR_Baseline") %>%
  
    pluck("levn_test")
```


```{r}
nested_processed
```

## check again descriptive stats

```{r}
nested_processed %>% 
  filter(Parameters == "SR_Baseline") %>% 
  pluck("described", 1) #%>% 
  # filter(!Condition == "Vehicle")

########## Save the output #########
   # write_csv(here("output_results", 
   #               "perme_cells",
   #               "SR_calcium",
   #               "baseline",
   #               paste(format(Sys.time(),
   #                            '%Y%m%d'),
   #                     "descriptive_summary_stats.csv",
   #                     sep = "_")))
```

# 7. Make anova and mix model(s)
 
```{r}
anova1 <- function(my_dataset){
  # rstatix::anova_test(value ~ Animal + Condition, data = my_dataset)
  # car::Anova(lm(value ~ Animal + Condition, data = my_dataset), type = "III")
  lm(value ~ Animal + Condition, data = my_dataset)
}

# exclude model with interactions.

# anova2 <- function(my_dataset){
#   # rstatix::anova_test(value ~ Animal * Condition, data = my_dataset)
#   # car::Anova(lm(value ~ Animal * Condition, data = my_dataset), type = "III")
#   lm(value ~ Animal * Condition, data = my_dataset)
#   # lm(value ~ Condition_grouped, 
#   #    data = my_dataset)
# }

mixm_1 <- function(my_dataset){
  lmerTest::lmer(value ~ Animal + Condition + (1|Animal_No), 
                 data = my_dataset,
                 REML = FALSE)
}

# exclude model with interactions.

# mixm_2 <- function(my_dataset){
#   lmerTest::lmer(value ~ Animal * Condition + (1|Animal_No), 
#                  data = my_dataset,
#                  REML = FALSE)
# }

mixm_3 <- function(my_dataset){
  lmerTest::lmer(value ~ Animal + Condition + (1|Animal_No/permeabilization), 
                 data = my_dataset,
                 REML = FALSE)
}

modeled_data <- nested_processed %>% 
  filter(Parameters == "SR_Baseline") %>% # Select only the baseline
  apply_model_func(my_model = anova1) %>%
  # apply_model_func(my_model = anova2) %>% # exclude model with interactions.
  apply_model_func(my_model = mixm_1) %>% 
  # apply_model_func(my_model = mixm_2) %>%  # exclude model with interactions.
  apply_model_func(my_model = mixm_3) %>% 
  pivot_longer(cols = contains(c("anova", "mix")), 
               names_to = "model_name", 
               values_to = "model_obj") %>% 
  mutate(est_mmeans = map(model_obj, ~ emmeans(.x, 
                                               specs = pairwise ~ Animal + Condition,  adjust = "BH")))
  

modeled_data %>% 
  head(1) %>% 
  pull(est_mmeans) %>% 
  pluck(1) %>% 
  summary

```



#7.1 Models performance
 
```{r}
model_performance <- modeled_data %>% 
  mutate(glance = map(model_obj, ~ broom.mixed::glance(.x))) %>% # NOTE: use {broom.mixed} when working with mixed models, otherwise throw error. 
  mutate(tidy = map(model_obj, ~ broom.mixed::tidy(.x))) %>% # NOTE: use {broom.mixed} when working with mixed models, otherwise throw error. 
  mutate(augment = map(model_obj, ~ broom.mixed::augment(.x))) %>% # NOTE: use {broom.mixed} when working with mixed models, otherwise throw error. 
  mutate(logLik = (glance %>% map_dbl(~ .x$logLik * -2)),
         AIC = (glance %>% map_dbl(~ .x$AIC)),
         BIC = (glance %>% map_dbl(~ .x$BIC)),
         # p_val = (glance %>% map_dbl(~ .x$p.value)),
         # sigma = (glance %>% map_dbl(~ .x$sigma))) %>% 
         p_val = map(model_obj,  ~(.x %>%
                                 car::Anova(type = "III") %>%
                                 broom::tidy())))# %>% 
  # pluck("glance", 3)
  # pluck("p_val")
  model_performance
```

```{r}
model_performance %>% 
  filter(model_name == "anova1") %>% 
  filter(dataset_type == "raw_data") %>% 
  pull(augment)
  # pull(augment)
  # filter(model_name == "mixm_1")
  # filter(model_name == "mixm_3")
  
```
