---
title: "Automatic report"
author: "Ruben Lopez"
date: "Generated on: `r format(Sys.time(), '%d.%m.%Y')`"
output:
  html_document: default
editor_options:
  chunk_output_type: inline
params:
  output_results: FALSE
---

# Analysis of luminal SR Ca^2+^ in permeabilized cells

### This document contain the following: 

- 1. [x] Descriptive statistics on wave parameters in intact cell 

- 2. [x] Hypothesis testing using linear regression with mixed effect model

- 3. [x] Superplots figures 


```{r, setup, echo=FALSE}
## Setting enviroment
knitr::opts_chunk$set(
  comment = '', fig.width= 6, fig.asp = 0.8, warning=FALSE, message=FALSE, results='hide', include=FALSE, echo=FALSE)
```

your parameter `r params$output_results`

------------------------------------------------------------------------

```{r}

############# Importing libraries #############

pacman::p_load(AnlysisOfWaves, # custom functions for analysis and loading of additional libraries
               here, fs, # folder's system navigation,
               readxl,readr,
               cowplot,
               dplyr, tidyr, purrr, stringr, forcats, # io of tabular files,
               # cowplot,
               # purrr, dplyr, tidyr, stringr, 
               kableExtra, # wrangling data
               ggplot2, ungeviz, # piloting
               lmerTest, broom.mixed, emmeans) # tools for mixed effect model computation and multiple comparison

options("scipen" = 999, "digits" = 4)


```


```{r}
############# Create folder and names structure #############

# name of parameters for analysis
parameters <- list("SR_calcium") %>% 
                                purrr::set_names()


# name of output directories for each parameter
output_results_dir <- map(parameters, ~(sprintf(here("results",
                               "perme_cells",
                               "%s"), .x)))

# name of figure directories for each parameter
output_figs_dir <- map(parameters, ~(sprintf(here("figures",
                                                  "perme_cells",
                                                  "%s"), .x)))

table_output_font_size = 10
```

```{r, eval=params$output_results}

# Create all new directories for output results and figures
c(output_results_dir, output_figs_dir) %>% 
  map(~dir_create(path = .x))

```
#### define variable namespace for ploting and directories

```{r}

SR_parameters <- c("SR_tau", "SR_DFF0", "SR_Baseline") %>% 
  rlang::set_names()

# experiment_dir <- "/Volumes/RUBEN FILES/Ruben/Work/GroupNiggli/Confocal/%s/SR_experiments"
# years <- c(2019, 2021, 2022)
# expe_dir_list <- map_chr(years, ~ sprintf(experiment_dir, .x))

```


## Load the Newest* local SR raw data from the csv file. 

NOTE: Check always the last date!!!


```{r}
raw_sr_data <- read_csv(file = paste(here("datasets",
                                          "perme_cells",
                                          "SR_calcium",
                                          paste("2022-03-17",
                                                "SR_raw_data.csv", sep = "_"))), # Check always the last date!!!
                        col_types = str_c(c(rep("f", 11), # convert to factors collumns 1 to 11
                                            "_", # skip column "Blank_SR_col"
                                            rep("d", 4)), # coerce to double the numeric variables
                                          collapse = "")) %>% 
  mutate(Animal = fct_relevel(Animal, "CPVT-HET", after = 1))

raw_sr_data %>% 
  glimpse()

# levels(raw_sr_data$Animal)
```

#### cleaning raw dataset

```{r}
raw_sr_data <- raw_sr_data %>% 
  filter(Condition != "Control") %>% # remove control and old experiments with 3 min incubation
  filter(!Inc_time_min %in% c(3)) %>% # remove control and old experiments with 3 min incubation
  select(-Treatment) %>% # remove repeated column
  filter(!(Date == "2019-10-25" & Experiment == "P2 CS3")) %>% # in this experiment cells did not react to drug (Fab)
  filter(!(Date == "2019-10-22" & Experiment == "P4 CS2")) %>% # this is a very obvious outlier in the dataset.
  filter(!(Date == "2019-10-31" & Experiment == "P3 CS3"))  %>% # Movement at caffeine application. Removed from dataset (vehicle).
  filter(!(Date == "2022-02-02" & Experiment == "P4 CS4"))  # this is an outlier in the dataset (vehicle)

```


#### aggregate by cell



```{r}

by_cell_df <- raw_sr_data %>% 
  summarize_sr_by_cell_func()

by_cell_df %>% 
  glimpse()
```

# Load Miguel data alone (already averaged by cell) and join with your aggregated-by-cell dataset



```{r}
## load Miguel's data

Migule_SR_df <- read_csv(here("datasets",
                              "perme_cells",
                              "SR_calcium",
                              "2022-01-07_Miguel_SR_measurements.csv"),
                         col_types = str_c(c(rep("f", 6), 
                                             rep("d", 3)), 
                                           collapse = ""),
                         show_col_types = FALSE) %>% 
  add_Treatment_factor_func() %>% 
  mutate(Treatment = factor(Treatment)) %>% # set to factor treatment
  rename_with(~ str_sub(.x, end = -6), .cols = ends_with("mean")) # remove sufix of colnames


## join Miguel and your aggregated dataset


pooled_sr_df <- by_cell_df %>% 
  left_join(select(Migule_SR_df, -Treatment))

pooled_sr_df %>%
  glimpse()

```

### checking the files for repository (take only your dataset) ->  done 

```{r eval=FALSE}
by_cell_df %>% 
  names
```


```{r eval=FALSE}
by_cell_df %>% 
  # names
  # distinct(filename) %>% 
  distinct(Date) %>%
  arrange(desc(.))
```

```{r, eval=FALSE}
by_cell_df %>%
  distinct(Date) %>%
  arrange(desc(.)) %>%
  mutate(Date = as.character(Date)) %>%
  mutate(Date = str_sub(Date, start = -8) %>% str_replace_all(pattern = "-", "")) %>%
  write_csv(file = "SR_calcium_dates.csv")
```



lest have a  look at the combined data

```{r results='show', include=TRUE}
pooled_sr_df %>% 
  kable %>%
  kable_styling(font_size = table_output_font_size) %>% 
  # collapse_rows(columns = c(1:5)) %>% 
  scroll_box(width = "100%", height = "400px")
```


 Create the permeabilization variable again for later be used in the mix model

```{r}

pooled_sr_df <- pooled_sr_df %>% 
  # mutate(Permeabilization = str_sub(Experiment, start = 1, end = 2))
  mutate(permeabilization = factor(paste(Animal_No, str_sub(Experiment, start = 1, end = 2), sep = "_"))) 

pooled_sr_df %>% 
  distinct(Animal, Condition)
```



# Hirarchical test

## Nest the df to asses asumption:

- Independence (done)
- No outliers 
- Normality -> ok
- qq plot (only visual)
- Homogeneity of variance: this is not assumed, so we apply simple transformation to the mean and center the data to check if improve model performance 


 
 
```{r}
nested_df <- pooled_sr_df %>%
# pooled_sr_df %>%
  
  # names
  pivot_longer(cols = where(is.double), names_to = "Parameters", ) %>% 
  group_by(Parameters) %>% 
  nest() %>% 
  rename(raw_data = data) %>% 
   # apply a transformation of the data = centering the dataset around the mean
  mutate(centered_data = map(raw_data, ~ .x %>%
                               group_by(Animal, Condition) %>%
                               mutate(value = value - mean(value)) %>% 
                               ungroup)) %>% 
  mutate(log10_data = map(raw_data, ~ .x %>%
                               group_by(Animal, Condition) %>%
                               mutate(value = log10(value)) %>% 
                               ungroup)) %>% 
  filter(Parameters == "SR_Baseline") %>% 
  pivot_longer(cols = ends_with("data"), names_to = "dataset_type", values_to = "data")


nested_df
```

### create Levene's test for homogeneity of variance test across groups
 
```{r}

levn_test <- function(my_dataset){
  car::leveneTest(value ~ Animal * Condition, data = my_dataset) # *** NOTE: from the description: If y is a linear-model object or a formula, the variables on the right-hand-side of the model must all be factors and must be completely crossed
  # bartlett.test(value ~ interaction(Animal , Condition), data = my_dataset)
}

```
 

# Describe and transform nested data: exploratory analysis
 
```{r}

nested_processed <- nested_df %>% 
  describe_nested_df("data") %>% # create descriptive statistics, outliers and qqplots
  apply_model_func(my_model = levn_test) %>% # apply homo_varianc leven test
  mutate(levn_test = map(levn_test, ~ .x %>% tidy())) # make the leven test tidy
  
nested_processed

```

## Q-Q plots


```{r, results='show', include=TRUE, collapse = TRUE, fig.width=12, fig.asp = 0.5, out.width='100%'}
nested_processed %>% 
  ungroup() %>% 
  filter(dataset_type == "raw_data") %>% 
  mutate(qq_plot = map(qq_plot, ~.x +  
                         ggplot2::scale_colour_manual(values = c("#666666", 
                                                                 "#CC0000")) +
                         ggplot2::scale_fill_manual(values = c("#666666", 
                                                                 "#CC0000")) +
                         pptx_presentation_theme_func(base_size = 12))) %>%
  pull(qq_plot) %>% 
  plot_grid(plotlist = ., ncol = 1)
```

## Check for Outliers

```{r results='show', include=TRUE}

# {r results='show', include=TRUE}
# pooled_sr_df %>% 
#   kable %>%
#   kable_styling(font_size = table_output_font_size) %>% 
#   collapse_rows(columns = c(1:5)) %>% 
#   scroll_box(width = "100%", height = "400px")


 nested_processed %>% 
  filter(dataset_type == "raw_data") %>% 
   pluck("outliers", 1) %>% 
   kable %>%
   kable_styling(font_size = table_output_font_size) %>% 
   # collapse_rows(columns = c(1:5)) %>% 
   scroll_box(width = "100%", height = "200px")
    # pluck("described")
    # pluck("qq_plot")
```


## check for Homogeneity of Variance 



```{r results='show', include=TRUE}
nested_processed  %>% 
  filter(dataset_type == "raw_data") %>% 
  pluck("levn_test", 1)  %>% 
  kable %>%
  kable_styling(font_size = table_output_font_size) %>% 
  # collapse_rows(columns = c(1:5)) %>% 
  scroll_box(width = "100%", height = "100px")
```



## check descriptive stats

```{r results='show', include=TRUE}
nested_processed %>% 
  filter(Parameters == "SR_Baseline") %>% 
  pluck("described", 1) %>% 
  kable %>%
  kable_styling(font_size = table_output_font_size) %>% 
  # collapse_rows(columns = c(1:5)) %>% 
  scroll_box(width = "100%", height = "300px")
  # filter(!Condition == "Vehicle")

########## Save the output #########
   # write_csv(here("output_results", 
   #               "perme_cells",
   #               "SR_calcium",
   #               "baseline",
   #               paste(format(Sys.time(),
   #                            '%Y%m%d'),
   #                     "descriptive_summary_stats.csv",
   #                     sep = "_")))
```

```{r eval = params$output_results}

nested_processed %>% 
  mutate(described = map2(Parameters, described, ~ .y %>% 
                         mutate(Parameters = .x))) %>% 
  filter(Parameters == "SR_Baseline") %>% 
  pluck("described", 1) %>% 
  ########## Save the output #########
   write_csv(here(output_results_dir,
                 paste(format(Sys.time(),
                              '%Y%m%d'),
                       parameters,
                       "descriptive_summary_stats.csv",
                       sep = "_")))


```



# Make anova and mix model(s)

these are the tested model tested
 
```{r include=TRUE, echo=TRUE}
anova1 <- function(my_dataset){
  # rstatix::anova_test(value ~ Animal + Condition, data = my_dataset)
  # car::Anova(lm(value ~ Animal + Condition, data = my_dataset), type = "III")
  lm(value ~ Animal + Condition, data = my_dataset)
}

# exclude model with interactions.

# anova2 <- function(my_dataset){
#   # rstatix::anova_test(value ~ Animal * Condition, data = my_dataset)
#   # car::Anova(lm(value ~ Animal * Condition, data = my_dataset), type = "III")
#   lm(value ~ Animal * Condition, data = my_dataset)
#   # lm(value ~ Condition_grouped, 
#   #    data = my_dataset)
# }

mixm_1 <- function(my_dataset){
  lmerTest::lmer(value ~ Animal + Condition + (1|Animal_No), 
                 data = my_dataset,
                 REML = FALSE)
}

# exclude model with interactions.

# mixm_2 <- function(my_dataset){
#   lmerTest::lmer(value ~ Animal * Condition + (1|Animal_No), 
#                  data = my_dataset,
#                  REML = FALSE)
# }

mixm_3 <- function(my_dataset){
  lmerTest::lmer(value ~ Animal + Condition + (1|Animal_No/permeabilization), 
                 data = my_dataset,
                 REML = FALSE)
}


```

We apply the model and check the output. Now in our grouped nested df is contained the model objects.

```{r }

model_raw_nsdf <- nested_processed %>% 
  filter(Parameters == "SR_Baseline") %>% # Select only the baseline
  apply_model_func(my_model = anova1) %>%
  # apply_model_func(my_model = anova2) %>% # exclude model with interactions.
  apply_model_func(my_model = mixm_1) %>% 
  # apply_model_func(my_model = mixm_2) %>%  # exclude model with interactions.
  apply_model_func(my_model = mixm_3) %>% 
  pivot_longer(cols = contains(c("anova", "mix")), 
               names_to = "model_name", 
               values_to = "model") #%>% 
  # mutate(est_mmeans = map(model, ~ emmeans(.x, 
  #                                              specs = pairwise ~ Animal + Condition,  adjust = "BH")))
  

# modeled_data %>% 
#   head(1) %>% 
#   pull(est_mmeans) %>% 
#   pluck(1) %>% 
#   summary

model_raw_nsdf
```


## Checking models performance
 
Then, we extract information and inspect side-by-side model performance.

```{r}
model_results_nsdf <- model_raw_nsdf %>%
# model_raw_nsdf %>% 
  # filter(dataset_type == "raw_data") %>% 
  # select(data) %>% 
  extract_model_info_func() %>% 
  plot_residuals_func()

model_results_nsdf
```
```{r}
model_results_nsdf
```
```{r results='show', include=TRUE, collapse = TRUE, fig.width=22, fig.asp = 0.5, out.width='200%'}

model_results_nsdf$dataset_type %>% 
  unique() %>% 
  map(~(model_results_nsdf %>% 
          # group_by(dataset_type) %>% 
          filter(dataset_type == .x ) %>%
          pull(res_vs_fit_plot) %>% 
          plot_grid(plotlist = ., 
                    ncol = 3, 
                    labels = paste0("dataset = ",.x), 
                    label_size = 16, label_x = 0.3))) %>% 
  plot_grid(plotlist = ., ncol = 1)
  
```

And here we can quickly look at the model performance

```{r results='show', include=TRUE}
model_results_nsdf %>% 
  select(where(is.character) | where(is.double)) %>% 
  kable %>%
  kable_styling(font_size = table_output_font_size) %>% 
  # collapse_rows(columns = c(1:5)) %>% 
  scroll_box(width = "100%", height = "400px")
```

# Contrasts and estimated marginal means 

### Make Contrast



we first create the marginal means object and then we design a matrix to make the desired comparisons. Here we want to compare genotypes differences among control and or drug application under different drugs, so we design the matrix accordingly



```{r}
model_results_nsdf$data[[1]]

```


```{r}


emmens_ns_df <- model_raw_nsdf %>%
  # model_raw_nsdf %>%
  # filter(str_detect(model_name, "no")) %>% 
  mutate(em_means = map2(data, model, ~ emmeans(object =  .y, 
                                                        specs =  ~ Animal * Condition, 
                                                        data = .x)),
         estimates = map(em_means, ~(.x %>%
                                       as_tibble %>%
                                       drop_na %>%
                                       mutate(across(where(is.double),
                                                     ~ round(.x, digits =2)))))) 
# we explore the size of the coeficient matrix
emmens_ns_df %>% 
  mutate(coef_grid = map(em_means, ~coef(pairs(.x)))) %>% 
  select(model_name, coef_grid) %>% 
  pluck("coef_grid", 1)
```
and here we designe our final matrix for comparison

```{r}
contrast_matrix <- list("WT_cAMP vs WT_Fab" = 
                          c(0, 0, 1, 0, 0, 0) - c(0, 0, 0, 0, 1, 0),
                          
                        "CPVT_cAMP vs CPVT_Fab" = 
                          c(0, 0, 1, 0, 0, 0) - c(0, 0, 0, 0, 1, 0))


contrast_matrix
```
store the comparisons aka contrasts

```{r}
emmens_ns_df <- emmens_ns_df %>% 
  mutate(contrast = map(em_means, ~(contrast(object = .x, 
                                             # method = "pairwise",
                                             method = contrast_matrix, # error when using custom matrix innested model with the "/" symbol. check above in the definition of teh model
                                             adjust = "BH") %>% 
                                      broom::tidy() %>%
                                      rstatix::add_significance(p.col = "adj.p.value", # adding p-significance symbols
                                                                output.col = "significance") %>%
                                      mutate(across(where(is.double),
                                                    ~ round(.x, digits =2)))
                                    
  ))) 
  
emmens_ns_df
```

Let's have a look at our contrast table in the interaction model.

```{r results='show', include=TRUE}
emmens_ns_df %>% 
  ungroup() %>% 
  # filter(!str_detect(model_name, "nointer")) %>% #take only the model with interaction
  select(Parameters, dataset_type, contrast, model_name) %>% 
  unnest(cols = c(contrast)) %>%
  mutate(group1 = word(contrast, 1),
         group2 = word(contrast, 3)) %>% 
  # pivot_longer(cols = starts_with("group"), names_to = "groups", values_to = "Condition") %>%
  # mutate(Animal = str_extract(Condition, pattern = "WT|CPVT"),
  #        Condition = str_extract(Condition, pattern = "Control|ISO")) %>%
  # pivot_wider(values_from = Animal, names_from = groups) %>%
  relocate(starts_with(c("model", "group")), .after = term) %>%
  select(-contrast, -null.value) %>%
  kable %>%
  kable_styling(font_size = table_output_font_size)

```


### Export results


Here we export the test contrast from the wave kinetics parameters: `r SR_parameters[3]` and can be found under the directory: `r output_results_dir$SR_calcium`


```{r eval = params$output_results}
emmens_ns_df %>% 
  filter(str_detect(dataset_type, "raw_data")) %>% # take stimations from raw data
  filter(str_detect(model_name, "mixm_1")) %>% # take the simplest mix model
  pull(contrast) %>% 
  # length()
  walk2(.x = ., 
        .y = SR_parameters[3],
        ~write_csv(x = .x, file = here(output_results_dir$SR_calcium, 
                                      paste(format(Sys.time(),
                                                   '%Y%m%d'), 
                                            .y, 
                                            "contrast.csv", sep = "_"))))
  

```


# Ploting 

## Superplots


```{r}
nested_df
```


```{r, results='show', include=TRUE, collapse = TRUE, fig.width=22, fig.asp = 0.3, out.width='100%'}

pmap(list(nested_df$data, 
          nested_df$Parameters, 
          nested_df$dataset_type), 
     function(data, parameters, dataset_type){
       data %>% 
         filter(Condition != "Vehicle") %>%
         multi_plot_list_func(yaxe_vars = "value",
                              # my_plot_fun = my_boxplot_and_jitter_func, 
                              my_plot_fun = superplot_func, 
                              base_violin = "waves",
                              dot_layer = "cells",
                              animal_layer = TRUE,
                              animal_size = 10,
                              cell_size = 5,
                              # wave_size = 2,
                              animal_alpha = 0.4,
                              faceted_by_1 = "Condition") %>% 
         `[[`(1)  +
         stat_summary(
           aes(color = Animal),
           size = 2,
           geom = "hpline",
           fun.y = "mean",
           # col = "black",
           size = 2,
           alpha = .5,
           # linetype="dashed",
           # shape = "-",
           # fill = "red"
         ) +
         labs(title = dataset_type, 
              y = parameters)
       
     }) %>% 
  plot_grid(plotlist = .,
            nrow = 1)
```


export plots

plots can be found in this directory `r output_figs_dir$SR_calcium`

```{r eval = params$output_results}
(nested_df$data[[1]] %>% 
  filter(Condition != "Vehicle") %>% 
         filter(Condition != "Vehicle") %>%
         superplot_func(yaxe = "value",
                        # xaxe = "Condition",
                        faceted_by_1 = "Condition",
                        # my_plot_fun = superplot_func, 
                        base_violin = "cells",
                        dot_layer = "cells",
                        animal_layer = T,
                        line_size = 1.5,
                        animal_size = 7,
                        cell_size = 2.5,
                        cell_alpha = 0.4,
                        animal_alpha = 0.7,
                        base_font_size = 36) +
         
         stat_summary(
           aes(color = Animal),
           size = 2,
           geom = "hpline",
           fun.y = "mean",
           # col = "black",
           size = 2,
           alpha = .5,
         ) + 
  labs(y = nested_df$Parameters[[1]])) %>% 
  ggsave(plot = ., filename = here(output_figs_dir$SR_calcium,
                                   paste(format(Sys.Date(),
                                                "%y%m%d"),
                                         paste0(SR_parameters[3],
                                                ".pdf"),
                                         sep = "_")),
         device = "pdf",
         units = "cm",
         width = 54,
         height = 24)


```



\

<center>FIN</center>

\
\
\
