---
title: "Automatic report"
author: "Ruben Lopez"
date: "Generated on: `r format(Sys.time(), '%d.%m.%Y')`"
output:
  html_document: default
  word_document: default
editor_options:
  chunk_output_type: inline
---

# Quantification and Analysis of immunoblots of total RyR and RyR's phosphosites P2808, P2814 and P2030



### This document contain the following: 

- 1. [x] Descriptive statistics on wave parameters in intact cell 

- 2. [x] Hypothesis testing using linear regression with mixed effect model

- 3. [x] Superplots figures 



```{r, setup, echo=FALSE}
## Setting enviroment
knitr::opts_chunk$set(
  comment = '', fig.width= 6, fig.asp = 0.8, warning=FALSE, message=FALSE, results='hide', include=FALSE, echo=FALSE)

# change this variable to FALSE if no output results desired

output_results = FALSE
```


------------------------------------------------------------------------

```{r}

############# Importing libraries #############

pacman::p_load(AnlysisOfWaves, # custom functions for analysis and loading of additional libraries
               here, fs, # folder's system navigation,
               dplyr, tidyr, forcats, purrr,
               # readxl)
               ggplot2, ggpubr,
               readr)
               # cowplot,
               # purrr, dplyr, tidyr, stringr, kableExtra, # wrangling data
               # ggplot2, ungeviz, # piloting
               # lmerTest, broom.mixed, emmeans) # tools for mixed effect model computation and multiple comparison

options("scipen" = 999, "digits" = 4)

```




# Defining working directories for importing data and exporting results

```{r}
################ location of the file at the Niggli server ################

# my_server_path <- "/Volumes/GroupNiggli/Ruben/Western Blot/WB_dataset_summary.csv"

################ location of the file in a local machine ################

raw_data_dir <- here("datasets","Western_blots")


############# Create folder and names structure #############

# name of parameters for analysis
RyR_prots <- list("Total_RyR", "Phospho_RyR") %>%
                                purrr::set_names()

phospho_prots <- list("P2030", "P2808", "P2814") %>% 
  purrr::set_names()

# name of output directories for each parameter
output_results_dir <- map(RyR_prots, ~(here("results",
                               "Western_blots", .x)))
output_results_dir

# name of output directories for figures

output_figs_dir <- map(RyR_prots, ~(here("figures",
                               "Western_blots", .x)))

output_figs_dir
```


```{r, eval=output_results}
# Create all new directories for output results and figures

c(output_results_dir, output_figs_dir) %>% 
  map(~dir_create(path = .x))

map(phospho_prots, ~ here(output_figs_dir$Phospho_RyR, .x) %>% 
      dir_create(.))

map(phospho_prots, ~ here(output_results_dir$Phospho_RyR, .x) %>% 
      dir_create(.))
```

# Importing raw data and reformating

```{r}
my_data_set <- read_csv(here(raw_data_dir, 
                              "WB_dataset_summary.csv"),
                        local = locale(encoding = "latin1")) %>% 
  rename(Date_of_Run = 1,
         Animal = Animal_Gen) %>%
  mutate(across(1:5, factor)) %>%
  mutate(Animal = factor(case_when(Animal == "CPVT-WT" ~ "WT",
                            Animal == "CPVT-HET" ~ "CPVT"),
                         levels = c("WT", "CPVT"))) %>%
  mutate(Condition = factor(case_when(Condition == "Iso" ~ "ISO",
                                      Condition == "Control" ~ "Control"),
                            levels = c("Control", "ISO")))
# my_data_set
```


# Normalization 1 - Normalize each protein by their total Protein
divide each target protein by the total Portein. You must first normalize each lane to its total protein

```{r}
my_data_set_Norm_TotProt <- my_data_set %>% 
  group_by(Date_of_Run, Animal, Date_of_Birth, Animal_No, Condition) %>% 
  mutate(RyR = RyR / Tot_Pro_RyR,
         P2808 = P2808 / Tot_Pro_P2808,
         P2814 = P2814 / Tot_Pro_P2814,
         P2030 = P2030 / Tot_Pro_P2030)

# my_data_set_Norm_TotProt
```



# Internal Normalization
# split the all dataset in the differencts gels

```{r}
Gel_1 <- my_data_set_Norm_TotProt %>%
  filter(Date_of_Run == "08.10.19")

Gel_2 <- my_data_set_Norm_TotProt %>%
  filter(Date_of_Run == "30.10.19")

Gel_3 <- my_data_set_Norm_TotProt %>%
  filter(Date_of_Run == "26.11.19")

Gel_4 <- my_data_set_Norm_TotProt %>%
  filter(Date_of_Run == "03.12.19")

```


# Internal Normalization 1: 
Divide gels 2 3 4 by its own reference 

```{r}

Gel_1_reference <- Gel_1 %>% 
  filter(Animal_No == "6026",
         Condition == "ISO")

# Gel_1_reference # taking later for normalizing gel 2

Gel_1_2nd_reference <- Gel_1 %>% # taking later for normalizing -->> used for Gel 3 & 4
  filter(Animal_No == "6034",
         Condition == "Control")


# Gel_1 <- Gel_1 %>% 
#   transmute(P2808 = P2808 * Gel_1_reference$P2808,
#             P2814 = P2814 * Gel_1_reference$P2814,
#             P2030 = P2030 * Gel_1_reference$P2030)
# 


# GEL 2

Gel_2_reference <- Gel_2 %>% 
  filter(Animal_No == "6026",
         Condition == "ISO")

# Gel_2_reference

Gel_2 <- Gel_2 %>% 
  mutate(RyR = RyR / Gel_2_reference$RyR,
         P2808 = P2808 / Gel_2_reference$P2808,
         P2814 = P2814 / Gel_2_reference$P2814,
         P2030 = P2030 / Gel_2_reference$P2030)

# Gel_2


# GEL 3

Gel_3_reference <- Gel_3 %>% # --->>> new reference
  filter(Animal_No == "6034",
         Condition == "Control")

# Gel_3_reference

Gel_3 <- Gel_3 %>% 
  mutate(RyR = RyR / Gel_3_reference$RyR,
         P2808 = P2808 / Gel_3_reference$P2808,
         P2814 = P2814 / Gel_3_reference$P2814,
         P2030 = P2030 / Gel_3_reference$P2030)

Gel_3

# GEL 4

Gel_4_reference <- Gel_4 %>% # --->>> new reference
  filter(Animal_No == "6034",
         Condition == "Control")

Gel_4_reference

Gel_4 <- Gel_4 %>% 
  mutate(RyR = RyR / Gel_4_reference$RyR,
            P2808 = P2808 / Gel_4_reference$P2808,
            P2814 = P2814 / Gel_4_reference$P2814,
            P2030 = P2030 / Gel_4_reference$P2030)

Gel_4

```


# Internal Normalization 2: 
multiply  2, 3 & 4 by the external reference (gel 1)



```{r}
Gel_1_reference # -->> only used for Gel 2
Gel_2
Gel_2 <- Gel_2 %>% 
  mutate(RyR = RyR * Gel_1_reference$RyR,
            P2808 = P2808 * Gel_1_reference$P2808,
            P2814 = P2814 * Gel_1_reference$P2814,
            P2030 = P2030 * Gel_1_reference$P2030)



Gel_1_2nd_reference

Gel_3 <- Gel_3 %>% 
  mutate(RyR = RyR * Gel_1_2nd_reference$RyR,
            P2808 = P2808 * Gel_1_2nd_reference$P2808,
            P2814 = P2814 * Gel_1_2nd_reference$P2814,
            P2030 = P2030 * Gel_1_2nd_reference$P2030)

Gel_4 <- Gel_4 %>% 
  mutate(RyR = RyR * Gel_1_2nd_reference$RyR,
            P2808 = P2808 * Gel_1_2nd_reference$P2808,
            P2814 = P2814 * Gel_1_2nd_reference$P2814,
            P2030 = P2030 * Gel_1_2nd_reference$P2030)
```

re-Bind all gels 


```{r}
my_data_set_Norm_TotProt <- rbind(Gel_1, Gel_2, Gel_3, Gel_4) %>% 
  ungroup %>% 
  select(!starts_with("Tot")) %>% 
  # remove repeated values
  ungroup %>%
  pivot_longer(cols =  c(P2808:P2030),
               names_to = "Proteins",
               values_to = "Relative_value" ) %>%
  distinct(Relative_value, .keep_all = T) %>%
  pivot_wider(names_from = Proteins, values_from = "Relative_value")


my_data_set_Norm_TotProt
```

check individual experiment trending 


```{r}
my_data_set_Norm_TotProt %>% 
  select(!starts_with("P")) %>% 
  pivot_longer(cols =  RyR,
               names_to = "Protein",
               values_to = "Relative_value") %>% 
  # distinct(Relative_value, .keep_all = T) %>%
  ggplot(aes(x = Condition,
             y = Relative_value)) +
  # geom_boxplot(aes(color = Animal)) +
  geom_point(aes(color = Animal_No), ) +
  facet_grid(. ~ Protein + Animal) +
  geom_line(aes(group = Animal_No)) +
  stat_compare_means(paired = T, show.legend = F)
```

# Plot total RyR


```{r}
my_data_set_Norm_TotProt %>% 
  select(!starts_with("P")) %>%
  pivot_longer(cols =  RyR,
               names_to = "Protein",
               values_to = "Relative_value" ) %>%
  # average the ISO + Control replicates
  group_by(Date_of_Run, Animal, Date_of_Birth, Animal_No, Protein) %>% 
  summarise(across(where(is.double), mean), .groups = "drop") %>% 
  
  mutate(Animal = fct_relevel(Animal, c("CPVT", "WT"))) %>%
  ggplot(aes(x = Animal,
             y = Relative_value,
             fill = Animal,
             color = Animal)) +
###### Add single data point ######
    geom_point(shape = 21,
              alpha = 0.25,
              # size = 4,
              size = 2,
              position = position_jitterdodge(jitter.width = 0.5,
                                              seed = 999,
                                              dodge.width = 0.9),
              show.legend = F) +
###### Add mean + 1sd ######
  stat_summary(fun.data = "mean_sdl",
               fun.args = list(mult = 1),
               size = 2,
               alpha = 0.7,
               show.legend = F) +
###### Add p.value comparison ######
  # stat_compare_means(paired = F, # this compute p.values
  #                    show.legend = F,
  #                    label.y = 2) +
###### Add reference line ######
    geom_hline(yintercept = 1, 
             # color  = "grey",
             linetype = "longdash") +

  scale_fill_manual(values = c( "#CC0000", "#666666")) +
  scale_color_manual(values = c( "#CC0000", "#666666")) +
  facet_grid(Protein  ~ .) +
  theme(strip.text.y.right = element_text(angle = 0, size = 18, margin = margin(l = 1.5, unit = "cm"))) +
   # xlab(label = "") + # Remove axis title
   xlab(label = NULL) + # Remove axis title
   ylab(label = "Relative value") + # Remove axis title
  coord_flip(ylim = c(0.1, 3)) +
    
  pptx_presentation_theme_func(base_size = 18)


```
# Export plot of total RyR

```{r eval = output_results}
  ########## Save your plot ##########
  ggsave(filename = here(output_figs_dir$Total_RyR, 
                          paste(format(Sys.Date(),
                                       "%y%m%d"),
                                "WB_RyR_alone_dots.pdf",
                                sep = "_")),
         device = "pdf",
         units = "cm",
         # width = 23, # use this dimension reference for the paper images.
         # height = 17.6) # use this dimension reference for the paper images.
         width = 12,
         height = 11)


```

